Turbulence in compact to giant HII regions

### 2022-01-03 strucfunc_paper.tex
Javier changes 2022-01-02

The blue horizontal and vertical dashed lines show the true \(r_{0}\) and the value of \(\text{B}(r) / \sigma^2 = 1 \), respectively.
The colored dotted lines indicate the averages, taking into account all the divisions of each map, of the apparent \(r_ {0}\) and the apparent \(\sigma^2 \).
From this analysis it is clear that \(r_0\) and \(\sigma^ 2 \) decrease with respect to the true values as the size \(L\) of the observational box decreases. 
This analysis is performed on different maps (no images are shown) given a different power law in the velocity spectrum and different correlation lengths, giving the same results.

@@

Then we calculate the average velocity difference of the original map, \(\Delta v \), and the smoothed map,b\(\tilde{\Delta v}\), in the points \( x = \{0, \delta \} \).
This expansion gives a term that modifies the final form of the structure function, \(\text{\~B} (r)\), where the structure function without the seeing, \(\text{B}(r) \), is corrected by the term \(S_0(r; s_0)\) which has the form:

@@

The equation \ref{eq:seeingemp2} is used to correct the observational structure function, \(\text{B}(r)\).

>>>>

The blue horizontal and vertical dashed lines show the true \(r_{0}\) and the value of \(B(r) / \sigma^2 = 1 \), respectively.
The colored dotted lines indicate the averages, taking into account all the divisions of each map, of the apparent \(r_ {0}\) and the apparent \(\sigma^2 \).
From this analysis it is clear that \(r_0\) and \(\sigma^ 2 \) decrease with respect to the true values as the size \(L\) of the observational box decreases. 
This analysis is performed on different maps (no images are shown) given a different power law in the velocity spectrum and different correlation lengths, giving the same results.

@@

Then we calculate the average velocity difference of the original map, \(\Delta v \), and the smoothed map,b\(\tilde{\Delta v}\), in the points \( x = \{0, \delta \} \).
This expansion gives a term that modifies the final form of the structure function, \(~B (r)\), where the structure function without the seeing, \(B(r) \), is corrected by the term \(S_0(r; s_0)\) which has the form:

@@

The equation \ref{eq:seeingemp2} is used to correct the observational structure function, \(B(r)\).
